%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Experience}
%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}
%------------------------------------------------

\workexperienceentry
{Software Engineer II} % Job title
{Microsoft} % Organization
{Redmond, USA} % Location
{Agu. 2018 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Participated and lead design discussions to met customers needs. }
    \item {Elaborated experiments and gathered data to test features prototypes.}
    \item {Worked as a software reliability engineer in a scheduled rotation, being in charge of mitigating issues that customers face in the production environment.} 
    \item {Diagnostic and mitigated performance issues in the system.}
    \item {Onboarded and mentoring new team members and external contributors.} 
    \item {Participated in the creation of the team base knowledge,  elaborating the documentation of different parts of the system.}
    \item {Improved the quality of the system's code, refactoring services and introducing tests for critical scenarios.}
\end{cvitems}
}
{\textbf{Technical Environment:} C\#, Typescript, React, Redux, ASP.NET, SqlServer}

%------------------------------------------------

\workexperienceentry
{Software Developer} % Job title
{Mi9 Retail} % Organization
{North Miami, USA} % Location
{Oct. 2016 - Agu. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
    \item {Developed a system for the DevOps team, integrated with the continuous integration pipeline to deploy the company products directly on client's machines.}
    \item {Increased the UI responsiveness for DevOps administrative tools by replacing Javascript polling calls with Signal-R achieving a more real-time scenario.}
    \item {Introduced technologies like the Elastic Stack to improve the analysis of  product's feedback.}  
    \item {Highly involved with the QA team to adopt technologies like TestNg to implement automatic tests.}
    \item {Developed the UI of the application responsible for managing the clients' environments in Amazon App Stream.}
    \item {Responsible for maintaining the Security Service implementing new features and APIs.}
\end{cvitems}
}
{\textbf{Technical Environment:} C\#, AngularJS, ASP.NET, SqlServer}

%------------------------------------------------

\workexperienceentry
{Software Developer} % Job title
{Dofleini} % Organization
{La Habana, Cuba} % Location
{Aug. 2015 - Jan. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item {Developed an application to draw accident sketches on real locations using Google Maps API and
		Javascript.}
	\item {Implemented a Security Service using Java to provide authorization and authentication
	process for the company's solutions.}
	\item {Implemented a directive for angular to manage user permission through ACL.}
	\item {Implemented a service to keep track of changes on user's sensitive information using Java and MongoDB.}
\end{cvitems}
}
{\textbf{Technical Environment:} Java, Spring Boot, AngularJS, MongoDb, PostgreSQL}


%------------------------------------------------    

\workexperienceentry
{Software Developer, Junior Researcher} % Job title
{Study Center of Computational Maths} % Organization
{La Habana, Cuba} % Location
{Mar. 2014 - Nov.2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
	\item {Improved the visualization quality of simulations, implementing a variation of the original QuadTree data structure known as Restrictive QuadTree.}
	\item {Implemented an FT-Tree data structure to reduce the amount of data to be transported to the graphics card without losing visualization quality.}
	\item {Improved the memory management for the module responsible for the rendering process, implementing the Disposable pattern and using windows API to release memory under high demanding circumstances, resulting in smoother simulations.}
	\item {Designed, developed and documented a javascript library to visualize and process 3D simulation on web browsers
	using WebGL.}
	\item {Developed camera models using matrix algorithms.}
\end{cvitems}
}
{\textbf{Technical Environment:} C\#, Javascript, WebGL, OpenTK}
\end{cventries}